---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vicedumap

<!-- badges: start -->
<!-- badges: end -->

Vicedumap is a simple package containing sf objects for the Victorian Department of Education's Regions and Areas.

The Department of Education has four regions and 17 areas. 

Areas are groups of local government areas. 

Regions groups of areas.

We have used this simple aggregation to create sf objects by summarising objects obtains using `strayr::read_absmap("lga2021")`

## Installation

You can install the development version of vicedumap from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zerogetsamgow/vicedumap")
```

## region_map

The following plot shows a map of the four regions which are contained in `vicedumap::area_map`.

```{r region_map}
library(vicedumap)
library(tidyverse)
## basic region_map
ggplot(
  region_map,
  aes(geometry = geometry,
  fill = region_name)
  ) +
geom_sf()+
ggthemes::theme_map()+
theme(
  legend.position.inside = c(.7,.7)
  )

```



## area_map

The following plot shows a map of the 17 areas which are contained in `vicedumap::area_map`

```{r area_map}
## basic area_map
ggplot(
  area_map,
  aes(geometry = geometry,
  fill = area_name)
  ) +
geom_sf()+
ggthemes::theme_map()+
theme(
  legend.position = "right",
  legend.justification = "centre"
  )

```

## region_tbl

The package contains a third dataset `vicedumap::region_tbl` which shows the mapping of local government areas, to areas, to regions

```{r region_tbl}
## print full table of regions, areas and lgas
knitr::kable(
  region_tbl
)

```
